Move Schedules: Fast persistence computations in coarse dynamic settings \thanks{ \textbf{Funding:} This work was partially supported by the National Science Foundation through grants CCF-2006661 and CAREER award DMS-1943758. }

### 2022-02-07 move_schedules.tex
arxiv version

% \documentclass[review]{siamart190516} % for SICOMP 
\documentclass{article} % for arxiv 
\usepackage{arxiv}

@@

Fix reindexing  bijections $f_i : K_i \to K_{i+1}$. 
Each $f_i$ induces a bijection $f_i^\ast : [m] \to [m]$, or equivalently, a permutation of the index set $[m]$. For each pair of filtrations $(K_i, K_{i+1})$, we assign labels to the simplices of $K_i$ using the index set $[m]$ and relabel $K_{i+1}$ accordingly using $f_i$. Denote these permutations by $p$ and $q$. 
We compute the longest increasing subsequence (LIS) of $q$ and use this subsequence to recover a longest common subsequence (LCS) $\mathrm{LCS}(p,q)$. We pass $p$, $q$, and this LCS to our greedy scheduling algorithm, which returns as output an ordered set of move permutations  $\mathcal{S}$ of minimum size, which we call a \emph{schedule}.
Not all valid schedules are created equal:
some incur a much larger number of column operations,
even if they have a minimal number of moves. 
Minimizing schedule costs will be addressed in 
Section~\ref{sec:schedule_cost}.
We proceed to computing an $R=DV$ decomposition for the first filtration $K_1$, and then execute the moves stored in $\mathcal{S}$ in sequence, extracting their corresponding persistence diagrams along the way. During execution, we obtain a valid decomposition $R = DV$ for each filtration $K_1, K_2, \dots, K_n$.

@@

% REQUIRED: siamplain format
\bibliographystyle{siamplain}
\bibliography{move_schedules}

>>>>

\pdfoutput=1
% \documentclass[review]{siamart190516} % for SICOMP 
\documentclass{article} % for arxiv 
\usepackage{arxiv}

@@

Fix reindexing  bijections $f_i : K_i \to K_{i+1}$. 
Each $f_i$ induces a bijection $f_i^\ast : [m] \to [m]$, or equivalently, a permutation of the index set $[m]$. For each pair of filtrations $(K_i, K_{i+1})$, we assign labels to the simplices of $K_i$ using the index set $[m]$ and relabel $K_{i+1}$ accordingly using $f_i$. Denote these permutations by $p$ and $q$. 
We compute the longest increasing subsequence (LIS) of $q$ and use this subsequence to recover a longest common subsequence (LCS) $\mathrm{LCS}(p,q)$. We pass $p$, $q$, and this LCS to our greedy scheduling algorithm, which returns as output an ordered set of move permutations  $\mathcal{S}$ of minimum size, which we call a \emph{schedule}.
Not all valid schedules are created equal: some incur a much larger number of column operations, even if they have a minimal number of moves; we address this issue in Section~\ref{sec:schedule_cost}.
Given the set of schedules for each pair $(K_i, K_{i+1})$, we proceed to computing an $R=DV$ decomposition for the first filtration $K_1$, and then execute the moves stored in $\mathcal{S}$ in sequence. During execution, we obtain a valid decomposition $R = DV$ for each filtration $K_1, K_2, \dots, K_n$ from which we extract persistence diagrams along the way.

@@

% REQUIRED: siamplain format
%\bibliographystyle{siamplain}
\bibliographystyle{unsrt}
\bibliography{move_schedules}
